---
output:
  pagedown::html_paged:
    css: ["one-column-paged-academic.css",  "https://use.fontawesome.com/releases/v5.7.2/css/all.css"]
    number_sections: false
links-to-footnotes: true
#knit: pagedown::chrome_print
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(knitr)
library(lubridate)
library(glue)

cv_entries <- read_csv("cv_entries_new.csv") %>% 
  mutate(year_begin = year(mdy(date)),
         time_begin = str_c(month(mdy(date), label = TRUE), " ", year(mdy(date)))) %>%
  mutate(year_end = case_when(
    date_end == "present" ~ date_end,
    date_end != "present" ~ str_c(month(mdy(date_end), label = TRUE)," ", year(mdy(date_end))),
    !is.na(date_end) ~ str_sub(date_end, 1, 4),
    is.na(date_end) ~ date_end
  )) %>% mutate(year = str_c(time_begin, " --- ", year_end))

```




:::::: {.title-and-contact}

::: {.title}
<h1 class="title">Adell Newell</h1>
:::

<!-- contact info -->
<font size="2">
  <center> 
    (217\) 619-2362 | addienewell1\@gmail.com | linkedin.com\/in\/addie-newell
  </center>
</font>

::::::



<div>
  <font size="4">
    <a><strong>Bachelor of Data Science</strong></a>
    <a style="float:right">Brigham Young University - Idaho</a>
  </font><br/>
    <a><strong>Minor: Statistics, Cluster: Mathematics</strong></a>
    <a style="float:right">Projected Graduation: July 2023</a>
</div>




<div class="cv-entries">

## EXPERIENCE

<hr style="height:1.5px;border-width:0;color:gray;background-color:gray">

```{r}
cv_entries %>% 
  filter(type == 'work') %>% 
  mutate(additional_info = replace_na(additional_info, ""),
         additional_info2 = replace_na(additional_info2, "")) %>% 
  mutate(what = str_c("<span class='work-title'><strong>", what, '</strong><a style="float:right">', where, "</a></span><br> - ", additional_info, "<br>- ", additional_info2)) %>% 
  select(year, what) %>% 
  kable()

```


## TECHNICAL SKILLS

<hr style="height:1.5px;border-width:0;color:gray;background-color:gray">


R (including Tidyverse packages) for data science, statistical analysis, and visualization (1.5 years)<br>
Python for data science, including Pandas and Altair (1.5 years)<br>
Some experience using Scikit-learn and TensorFlow to create machine learning models<br>
Create, populate, and query databases with SQL (1 year), some experience with PL/SQL<br>
Some experience with Power BI, Excel, and other Microsoft Office products




